### 2012-10-15 notes.tex
Partially correct gamma1 update.

We are now able to decompose $\mathcal{L}$ into its constituent parts
\begin{multline}\label{eqn:composite}
\mathcal{L} = K\sum_{j=1}^J \E_q\log p(\mu_j|u_0,\sigma_0^2) + \sum_{j=1}^J\sum_{k=1}^K\E_q \log p(\theta_{kj} | \mu_j; M_0) 
+ \sum_{j=1}^J\sum_{k=1}^K\E_q \log p(r_{kj} | \theta_{kj}, n_{kj})\\
- K\sum_{j=1}^J\E_q \log q(\mu) - \sum_{j=1}^J\sum_{k=1}^K \E_q \log q(\theta_{kj})
\end{multline}

@@

\begin{align}
\E_q \log p(\theta_{kj} | \mu_j ; M_0) & = \int_{\mu_j} q(\mu_j) \int_{\theta_{kj}} q(\theta_{kj}) \log p(\theta_{kj} | \mu_j, M_0)\\
\begin{split}
& = \log \Gamma(M_0) - \E_q \log \Gamma(\mu_j M_0) - \E_q \log \Gamma((1-\mu_j)M_0) \\
& \qquad+(\gamma_{1j}M_0-1)\left( \psi(\alpha_{kj}) - \psi(\alpha_{kj} + \beta_{kj}) \right) \\
& \qquad + ((1-\gamma_{1j})M_0-1)\left( \psi(\beta_{kj}) - \psi(\alpha_{kj} + \beta_{kj}) \right)
\end{split}
\end{align}
where $\E_q \log \Gamma(\mu_j M_0)$ is easily computed numerically. In general, we will be able to differentiate under the integral by Leibniz integral rule and the fact that the bounds are constants $\mu_j \in [0,1]$.

@@

{\bf Update Equation for $u_0$ }

@@

Isolating terms that involve $\gamma_{2j}$ gives
\begin{equation*}
\mathcal{L}_{[\gamma_{1j}]} = -\frac{K}{2\sigma_0^2}(\gamma_{1j}-u_0)^2 
+ \sum_{k=1}^K \gamma_{1j} M_0 ( \psi(\alpha_kj) - \psi(\alpha_{kj} + \beta_{kj}) )
- \sum_{k=1}^K \gamma_{1j} M_0 ( \psi(\beta_kj) - \psi(\alpha_{kj} + \beta_{kj}) )
\end{equation*}

Taking the derivative with respect to $\gamma_{1j}$, setting it equal to zero and solving for $\gamma_{1j}$ gives
\begin{equation}
\gamma_{1j} \leftarrow u_0 + M_0 \sigma_0^2 \frac{1}{K} \sum_{k=1}^K \psi(\alpha_{kj}) - \psi(\beta_{kj})
\end{equation}

>>>>

%%%			log-likelihood bound			%%%
We are now able to decompose $\mathcal{L}$ into its constituent parts
\begin{multline}\label{eqn:composite}
\mathcal{L} = K\sum_{j=1}^J \E_q\log p(\mu_j|u_0,\sigma_0^2) + \sum_{j=1}^J\sum_{k=1}^K\E_q \log p(\theta_{kj} | \mu_j; M_0) 
+ \sum_{j=1}^J\sum_{k=1}^K\E_q \log p(r_{kj} | \theta_{kj}, n_{kj})\\
- K\sum_{j=1}^J\E_q \log q(\mu) - \sum_{j=1}^J\sum_{k=1}^K \E_q \log q(\theta_{kj})
\end{multline}

@@

\begin{align}
\E_q \log p(\theta_{kj} | \mu_j ; M_0) & = \int_{\mu_j} q(\mu_j) \int_{\theta_{kj}} q(\theta_{kj}) \log p(\theta_{kj} | \mu_j, M_0)\\
\begin{split}
& = \log \Gamma(M_0) -\E_q \log \Gamma(\mu_j M_0) -\E_q \log \Gamma((1-\mu_j)M_0) \\
& \qquad+(\gamma_{1j}M_0-1)\left( \psi(\alpha_{kj}) - \psi(\alpha_{kj} + \beta_{kj}) \right) \\
& \qquad + ((1-\gamma_{1j})M_0-1)\left( \psi(\beta_{kj}) - \psi(\alpha_{kj} + \beta_{kj}) \right)
\end{split}
\end{align}
where $\E_q \log \Gamma(\mu_j M_0)$ is easily computed numerically. In general, we will be able to differentiate under the integral by Leibniz integral rule and the fact that the bounds are constants $\mu_j \in [0,1]$.

@@

%%%			u0 update				%%%
{\bf Update Equation for $u_0$ }

@@

Isolating terms that involve $\gamma_{1j}$ gives
\begin{multline*}
\mathcal{L}_{[\gamma_{1j}]} = -\frac{K}{2\sigma_0^2}(\gamma_{1j}-u_0)^2 
-\E_q \log \Gamma(\mu_j M_0) -\E_q \log \Gamma((1-\mu_j)M_0) \\
+ \sum_{k=1}^K \gamma_{1j} M_0 ( \psi(\alpha_kj) - \psi(\alpha_{kj} + \beta_{kj}) )
- \sum_{k=1}^K \gamma_{1j} M_0 ( \psi(\beta_kj) - \psi(\alpha_{kj} + \beta_{kj}) )
\end{multline*}

Taking the derivative with respect to $\gamma_{1j}$  gives
\begin{equation}
.
\end{equation}
